\LARGE \bf Multi-dimensional Optimization of Gasoline-fueled Variable Pitch Multirotor Aircraft

### 2016-03-24 paper.tex
optimization section work

Because the quad is going to be build using commercially available off the shell parts the optimization must be closely based on reality.  Ultimately that means we only can pick the size of engine that we are going to use.  All the other data about the engine (mass, maximum power, etc.) have to be a function of displacement size.  We collected data about popular two stroke RC aircraft engines from several sources to produce the below plots.

@@

@@

Second model used to develop the optimization framework for this project was based on an MIT lecture given on aircraft propeller performance given in \cite{mit2016}. In order to test the theory of this model and also to further the progress of the optimization model, only two of the design variables were chosen to optimize: rotor radius and fuel consumption rate, $f_{rate}$. Flight time was then calculated by 
\begin{equation}
	t_{flight} = f_{capacity}/f_{rate}.
\end{equation}
This allowed for a very easy calculation in which to test the optimization technique. Without constraints, the solution to maximizing flight time would be trivial. To properly use the constraints, power produced ($P_{prod}$), power required ($P_{req}$), thrust produced ($T_{prod}$), and thrust required ($T_{req}$) all had to be calculated to make sure that the rotor radius had a relationship to the fuel consumption rate. These calculations used some approximations in the rotor dynamics. The following calculations come from a MIT lecture on thermodynamics.

@@

What optimizers, setup, comparing matlab and python.

Figure of Pareto fronts...

constraint sensitivity - aerodynamics, engine efficiencies...

@@

\begin{itemize}
	\item{Table showing the optimal design parameters}
\end{itemize}

>>>>

Because the quad is going to be build using commercially available off-the-shelf parts the optimization must be closely based on reality.  This means we only can pick the size of engine that we are going to use.  All the other data about the engine (mass, maximum power, etc.) have to be a function of displacement size.  We collected data about popular two stroke RC aircraft engines from several sources to produce the below plots.

@@

Although the off-the-shelf constraint also applies to choosing the rotor parameters, continuous variables approximating the rotor specs are used and then analyzed as follows.

@@

Second model used to develop the optimization framework for this project was based on an MIT lecture given on aircraft propeller performance given in \cite{mit2016}. In order to test the theory of this model and also to further the progress of the optimization model, only two of the design variables were chosen to optimize: rotor radius and fuel consumption rate, $f_{rate}$.

To properly analyses the system, power required ($P_{req}$) and thrust produced ($T_{prod}$) have to be calculated to make sure that the rotor radius had a relationship to the fuel consumption rate. These calculations used some approximations in the rotor dynamics. The following calculations come from a MIT lecture on thermodynamics.

@@

Flight time was calculated by 
\begin{equation}
	t_{flight} = K_{energy}*f_{capacity}/f_{rate}.
\end{equation}
Without constraints, the solution to maximizing flight time would be trivial and impossible. To optimize the system we use the constraints on the power produced ($P_{prod}$), power required ($P_{req}$), thrust produced ($T_{prod}$), and lift required ($T_{req}$) all had to be calculated to make sure that the rotor radius had a relationship to the fuel consumption rate.

We then will discuss the following:
\begin{itemize}
	\item{scaling of the design variables}
	\item{how we got gradients}
	\item{the optimization method that we utilized}
\end{itemize}

So far our problem has been implemented both in python and in matlab.  Here we can talk about the benefits and challenges of using each.

Since we can only optimize for maximum flight time give a payload (parameter) we can further explore how the characteristics of a gas quad change as we optimize the flight time for different payloads. It may turn out that the optimal quad parameters change greatly as it is optimized for different flight times.  In this case we could choose several payloads and optimize over all of then together. \textit{We will present these results with a figure and some discussion.}

\begin{figurehere}
	\includegraphics[width=0.5\textwidth]{payload.jpg}
	\caption{Stand in figure showing optimal flight time as a function of payload.}
		\label{fig:payload}
\end{figurehere}

Here we can do some discussion on constraint sensitivity - aerodynamics, engine efficiencies...

@@

We have found that the flight time of a gas-quad can be maximized by constructing with the following design.

\begin{tablehere}
\centering
\begin{tabulary}{0.5\textwidth}{|C|C|C|C|C|C|}
\hline
       & displacement & fuel rate & rotor radius & other \\ \hline
  & 100 & 30 & 250 & 150 \\ \hline
\end{tabulary}
\caption{Optimal design variables}
\label{table:fw_loop_rates}
\end{tablehere}
